---
title: "Project Week 4"
author: "Joana"
date: "4 May 2018"
output: ioslides_presentation
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Data description
<font size="3">
Standardized fertility measure and socio-economic indicators for each of 47 French-speaking provinces of Switzerland at about 1888.
We have chosen SWISS dataset in R to visualize a potential relationship between its variables. 

1. Fertility	Ig, 'common standardized fertility measure'
2. Agriculture	% of males involved in agriculture as occupation
3. Examination	% draftees receiving highest mark on army examination
4. Education	% education beyond primary school for draftees.
5. Catholic	% 'catholic' (as opposed to 'protestant').
6. Infant.Mortality	live births who live less than 1 year.

Here, all variables are scaled to [0, 100], where in the original, all but "Catholic" were scaled to [0, 1]
</font>

## Aim
<h4>
**Goal**
</h4>
<h6>
Scatterplot of all the variables to check a possible relationship between its variables.
</h6>
<br>
<h4>
**How does it work:**
</h4>
</h6>
1. The user can select what variables he shall wish to look for a relationship.

2. Simultaneously the app will plot the linear regression analysis of such association.
</h6>

## App Visualization
<h4>
**Visualize the app**
</h4>

<h6>
To visualize the app, please redirect yourself to:

https://joanap08.shinyapps.io/swiss/
</h6>

## Interactive Plot
<h6>
In this  slide you are able to check pre-sample of the app
</h6>
```{r swiss}
library(ggplot2)
inputPanel(
      radioButtons("x", "Select X-axis:",
                   list("Fertility"='a', "Agriculture"='b', "Examination"='c', "Education"='d',"Catholic"='e',"Infant.Mortality"='f')),
      radioButtons("y", "Select Y-axis:",
                   list("Fertility"='g', "Agriculture"='h', "Examination"='i', "Education"='j',"Catholic"='k',"Infant.Mortality"='l'))
)

renderPlot({
    if(input$x=='a'){
      i<-1
    }
    
    if(input$x=='b'){
      i<-2
    }
    
    if(input$x=='c'){
      i<-3
    }
    
    if(input$x=='d'){
      i<-4
    }
    
    if(input$x=='e'){
      i<-5
    }
    
    if(input$x=='f'){
      i<-6
    }
    
    if(input$y=='g'){
      j<-1
    }
    
    if(input$y=='h'){
      j<-2
    }
    if(input$y=='i'){
      j<-3
    }
    if(input$y=='j'){
      j<-4
    }
    if(input$y=='k'){
      j<-5
    }
    if(input$y=='l'){
      j<-6
    }
    s    <- swiss[, i]
    k    <- swiss[, j]
    qplot(s,k,main="Relationship between Variables in the Swiss dataset",geom=c("point", "smooth"),xlab ="",ylab="" )
  
})

```


